Modelling results

### 2024-09-06 notebooks/02-modelling-results.qmd
Re-analyses finished, reports rendered, onto redaction

::: {#suppfig-corr-mat-questionnaires}
```{r}
#| label: corr-mat-questionnaires
#| fig-width: 10
#| fig-height: 6
#| eval: false

@@

corr_aph |> summary() |> plot() +
  labs(title = "Correlation matrix, aphantasia group only (Spearman FDR corrected)")

@@

corr_control |> summary() |> plot() +
  labs(title = "Correlation matrix, control group only (Spearman FDR corrected)")

@@

The quality checks of the models are displayed in @suppfig-implicit-checks[ and @suppfig-explicit-checks]{.content-visible when-format="html"} @suppfig-implicit-checks-2[ and @suppfig-explicit-checks-2]{.content-hidden when-format="html"}.

@@

The figures below are also displayed in the main article. \[See the HTML version for the code and details.\] {.content-hidden when-format="html"}

@@

(
  plot_models_full(subj_means_im, emmeans_im, y_min = 400, y_max = 1110, size = 4) +
  plot_models_zoomed(subj_means_im, emmeans_im, size = 4) &
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.text = element_text(size = 20),
    legend.margin = margin(0, 150, 25, 0),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 18)
  )
) +
  plot_layout(
    guides = "collect",
    widths = c(1, 1.2)
  )

@@

(
  plot_models_full(subj_means_ex, emmeans_ex, y_min = 350, y_max = 1450, size = 4) +
  plot_models_zoomed(subj_means_ex, emmeans_ex, size = 4) &
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.text = element_text(size = 20),
    legend.margin = margin(0, 150, 25, 0),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 18)
  )
) +
  plot_layout(
    guides = "collect",
    widths = c(1, 1.2)
  )

@@

# Finer groups

```{r}
#| label: checking-finer-groups

df_questionnaires |> 
  group_by(aphantasia, sub_group) |> 
  count() |> 
  arrange(sub_group)
```

Interestingly, we have 39 participants that did not score at floor VVIQ but between 17 and 32, a score range that @reeder have proposed to call "hypophantasia". However, our sample comprised only 2 hyperphantasics, i.e. participants scoring above 74 [@zeman2024]. These two participants will therefore be removed from the sample before performing new analyses on the aphantasic, hypophantasic and typical groups.

```{r}

@@

```{r}
#| label: checks
#| fig-width: 14
#| fig-height: 12
#| eval: false

@@

```{r}
model_performance(fit_finer_i)

model_parameters(fit_finer_i)
```

```{r}
model_performance(fit_finer_e)

model_parameters(fit_finer_e)
```

```{r}
#| label: emmeans-finer
#| echo: false

Anova(fit_finer_i, type = 3)
Anova(fit_finer_e, type = 3)

# emmeans_im <-
  emmeans(fit_finer_i, c("congruence", "sub_group")) |>
  summary(point.est = median) |>
  as_tibble() |>
  mutate(across(3:7, ~.*1000)) |>
  rename(median = emmean)

# emmeans_im |> 
#   rename(Group = 1, Condition = 2, "Median (ms)" = median) |>
#   display()

fit_finer_i |> 
  estimate_contrasts(
    contrast = c("congruence", "sub_group"), 
    p_adjust = "none"
  )

# emmeans_ex <-
  emmeans(fit_finer_e, c("congruence", "sub_group")) |>
  summary(point.est = median) |>
  as_tibble() |>
  mutate(across(3:7, ~.*1000)) |>
  rename(median = emmean)

fit_finer_e |> 
  estimate_contrasts(
    contrast = c("congruence", "sub_group"), 
    p_adjust = "none"
  )
```

>>>>

::: {#suppfig-corr-mat-questionnaires}
```{r}
#| label: corr-mat-questionnaires
#| fig-width: 10
#| fig-height: 6

@@

# corr_aph |> summary() |> plot() +
#   labs(title = "Correlation matrix, aphantasia group only (Spearman FDR corrected)")

@@

# corr_control |> summary() |> plot() +
#   labs(title = "Correlation matrix, control group only (Spearman FDR corrected)")

@@

The quality checks of the models are displayed in [@suppfig-implicit-checks and @suppfig-explicit-checks]{.content-visible when-format="html"} [@suppfig-implicit-checks-2 and @suppfig-explicit-checks-2]{.content-hidden when-format="html"}.

@@

The figures below are also displayed in the main article. [See the HTML version for the code and details.]{.content-hidden when-format="html"}

@@

(
  plot_models_full(subj_means_im, "aphantasia", emmeans_im, y_min = 400, y_max = 1110, size = 4) +
  plot_models_zoomed(subj_means_im, "aphantasia", emmeans_im, size = 4) &
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.text = element_text(size = 20),
    legend.margin = margin(0, 150, 25, 0),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 18)
  )
) +
  plot_layout(
    guides = "collect",
    widths = c(1, 1.2)
  )

@@

(
  plot_models_full(subj_means_ex, "aphantasia", emmeans_ex, y_min = 350, y_max = 1450, size = 4) +
  plot_models_zoomed(subj_means_ex, "aphantasia", emmeans_ex, size = 4) &
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.text = element_text(size = 20),
    legend.margin = margin(0, 150, 25, 0),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 18)
  )
) +
  plot_layout(
    guides = "collect",
    widths = c(1, 1.2)
  )

@@

# Finer sub-groups

::: {#supptbl-finer-check}
```{r}
#| label: checking-finer-groups

df_questionnaires |> 
  group_by(aphantasia, sub_group) |> 
  count() |> 
  arrange(sub_group) |> 
  rename(Aphantasia = 1, "Sub-group" = 2, N = 3) |> 
  display()
```
:::

Interestingly, we have 39 participants that did not score at floor VVIQ but between 17 and 32, a score range that @reeder have proposed to call "hypophantasia". However, our sample comprised only 2 hyperphantasics, i.e. participants scoring above 74 [@zeman2024]. These two participants will therefore be removed from the sample before performing new analyses on the aphantasic, hypophantasic and control groups.

```{r}
#| label: finer-models

@@

```{r}
#| label: checks-finer-models
#| fig-width: 14
#| fig-height: 12
#| eval: false

@@

![Model assumption checks for the Generalized Linear Mixed Model fit on the RTs in the implicit task with finer sub-groups.](../figures/checks-finer-implicit.png){#suppfig-implicit-checks-finer}

![Model assumption checks for the Generalized Linear Mixed Model fit on the RTs in the explicit task with finer sub-groups.](../figures/checks-finer-explicit.png){#suppfig-explicit-checks-finer}

::: {#supptbl-im-summary-finer}
```{r}
#| label: summary-finer-im

model_performance(fit_finer_i) |> display()

model_parameters(fit_finer_i) |> display()

# Anova(fit_finer_i, type = 3)
```
:::

::: {#supptbl-ex-summary-finer}
```{r}
#| label: summary-finer-ex

model_performance(fit_finer_e) |> display()

model_parameters(fit_finer_e) |> display()

# Anova(fit_finer_e, type = 3)
```
:::

::: {#supptbl-im-estimates-finer}
```{r}
#| label: emmeans-finer-im
#| echo: false

emmeans_finer_im <-
  emmeans(fit_finer_i, c("congruence", "sub_group")) |>
  summary(point.est = median) |>
  as_tibble() |>
  mutate(across(3:7, ~.*1000)) |>
  rename(median = emmean)

emmeans_finer_im |>
  rename(Condition = 1, "Sub-group" = 2, "Median (ms)" = median) |>
  display()

fit_finer_i |>
  estimate_contrasts(
    contrast = c("congruence", "sub_group"),
    p_adjust = "none"
  ) |> 
  display()
```
:::

::: {#supptbl-ex-estimates-finer}
```{r}
#| label: emmeans-finer-ex
#| echo: false

emmeans_finer_ex <-
  emmeans(fit_finer_e, c("congruence", "sub_group")) |>
  summary(point.est = median) |>
  as_tibble() |>
  mutate(across(3:7, ~.*1000)) |>
  rename(median = emmean)

emmeans_finer_ex |>
  rename(Condition = 1, "Sub-group" = 2, "Median (ms)" = median) |>
  display()

fit_finer_e |>
  estimate_contrasts(
    contrast = c("congruence", "sub_group"),
    p_adjust = "none"
  ) |> 
  display()
```
:::

```{r}
#| label: fig-finer-im
#| fig-width: 18
#| fig-height: 7

subj_means_finer_im <-
  df_i_finer |> 
  group_by(subjectid, sub_group, congruence) |>
  reframe(rt = mean(rt)*1000)

(
  plot_models_full(subj_means_finer_im, "sub_group", emmeans_finer_im, size = 4, dw = .6) +
  plot_models_zoomed(subj_means_finer_im, "sub_group", emmeans_finer_im, size = 4) &
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.text = element_text(size = 20),
    legend.margin = margin(0, 150, 25, 0),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 18)
  )
) +
  plot_layout(
    guides = "collect",
    widths = c(1, 1.2)
  )

# ggsave(here("figures/model-implicit-sub-groups.png"), dpi = 600)
```

```{r}
#| label: fig-finer-ex
#| fig-width: 18
#| fig-height: 7

subj_means_finer_ex <-
  df_e_finer |> 
  group_by(subjectid, sub_group, congruence) |>
  reframe(rt = mean(rt)*1000)

(
  plot_models_full(subj_means_finer_ex, "sub_group", emmeans_finer_ex, y_min = 350, y_max = 1450, size = 4, dw = .6) +
  plot_models_zoomed(subj_means_finer_ex, "sub_group", emmeans_finer_ex, size = 4) &
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    legend.text = element_text(size = 20),
    legend.margin = margin(0, 150, 25, 0),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 18)
  )
) +
  plot_layout(
    guides = "collect",
    widths = c(1, 1.2)
  )

# ggsave(here("figures/model-explicit-sub-groups.png"), dpi = 600)
```
